Group Theory in Physics (Course Note)

### 2016-11-12 Lecture note - Group Theory in Physics/sections/20161031.tex
Finished a proof of "irreducible repre" = "conjugacy class".

        We first look at the regular representation. The previous
        section shows (by equation \ref{eq:20161031-X_components},
        \ref{eq:20161031-X-characters}, and
        \ref{eq:20161031-X_components_reg}):
        \begin{equation}
            \sum_{i\in\text{ I.R.}} \chi^{i,1}\chi^{i,a} = N
            \delta_{a,e}
        \end{equation}
        Here $i$ denotes different irreducible representations, $a$
        for conjugacy classes. The delta function is $1$ only when $a$
        is the unit conjugacy class.

@@

        Now consider the class vectors:
        \begin{defi}[Class vector $\mathcal{K}_a$]
        \nomenclature{Class vector $\mathcal{K}_a$}{\nomrefpage.}
            \begin{equation}
                \mathcal{K}_a = \sum_{g\in K_a} g
            \end{equation}
            where $a$ represents the conjugacy class labeled
            by $K_a$.
        \end{defi}
        It has the following property: it is invariant under
        conjugation
        \begin{equation}
            h\mathcal{K}_a h^{-1} = \mathcal{K}_a
        \end{equation}
        since a conjugacy are those elements that can be related by a
        conjugation. From this, we have obviouisly
        \begin{equation}
            g\mathcal{K}_a \mathcal{K}_b g^{-1} = \mathcal{K}_a
            \mathcal{K}_b
        \end{equation}
        Thus $\mathcal{K}_a \mathcal{K}_b$ is also a set related to
        each other 
    \end{proof}
% 1. 自共轭 iff 特征 实数
% 2. 非自共轭 至少一个群元 复数 -》 成对出现
% 3. 实表示 是 自共轭
% 4. 特征 实数 不一定 实表示 (so 有 自共轭 但非 实的表示)
% 5. thm 5 on pp. 68.

>>>>

        We first look at the regular representation. The previous
        section shows (by equation \ref{eq:20161031-X_components},
        \ref{eq:20161031-X-characters}, and
        \ref{eq:20161031-X_components_reg}):
        \begin{equation}
            \sum_{i\in\text{ I.R.}} \chi^{i,1}\chi^{i,a} = N
            \delta_{a,e}
            \label{eq:20161031-x1xa-Ndelta}
        \end{equation}
        Here $i$ denotes different irreducible representations, $a$
        for conjugacy classes. The delta function is $1$ only when $a$
        is the unit conjugacy class.

@@

        Now consider the class vectors:
        \begin{defi}[Class vector $\mathcal{K}_a$]
        \nomenclature{Class vector $\mathcal{K}_a$}{\nomrefpage.}
            \begin{equation}
                \mathcal{K}_a = \sum_{g\in K_a} g
            \end{equation}
            where $a$ represents the conjugacy class labeled
            by $K_a$.
        \end{defi}
        It has the following property: it is invariant under
        conjugation
        \begin{equation}
            h\mathcal{K}_a h^{-1} = \mathcal{K}_a
            \label{eq:20161031-hKh-K}
        \end{equation}
        since a conjugacy class are those elements that can be related by a
        conjugation. From this, we have obviouisly
        \begin{equation}
            g\mathcal{K}_a \mathcal{K}_b g^{-1} = \mathcal{K}_a
            \mathcal{K}_b
        \end{equation}
        Thus $\mathcal{K}_a \mathcal{K}_b$ is also a vector whose
        components are related to
        each other with conjating like relations. It is then a linear
        combination of class vectors:
        \begin{equation}
            \label{eq:20161031-algebra-like-relation}
            \mathcal{K}_a\mathcal{K}_b = \sum_c c_{abc} \mathcal{K}_c
        \end{equation}
        where $c_{abc}$ are coefficients.
        (it is mentioned that such a form will make those classes an
        algebra, named class algebra\nomenclature{class
        algebra}{\nomrefpage}, but now I will not talk on that.

        Now, consider the class vectors $\mathcal{K}_a$ in certain
        irreducible representation $\mu$:
        \begin{equation}
            D^a_{(\mu)} := \sum_{g\in \mathcal{K}_a} D_{(\mu)}(g)
        \end{equation}
        It commutes with all $D_{(\mu)}(h)$, $h\in G$, since
        $$D_{(\mu)}(h) \sum_{g\in \mathcal{K}_a} D_{(\mu)}(g)
        D_{(\mu)}(h^{-1})= \sum_{g\in \mathcal{K}_a} D_{(\mu)}(g)$$
        Then by Schur's lemma, $D^a_{(\mu)}= \lambda^a_\mu
        \id$.
        Take the trace of $D^a_{(\mu)}$, one will easily find:
        \begin{equation}
            \label{eq:20161031-lambda-is}
            \lambda^a_\mu = \frac{n_a\chi^a_{\mu}}{\chi^1_\mu}
        \end{equation}
        Meanwhile, by the algebra like relation
        \ref{eq:20161031-algebra-like-relation}, one finds:
        \begin{equation}
            \lambda^a_\mu \lambda^b_\mu = \sum_c c_{abc} \lambda^c_\mu
        \end{equation}
        combine this with the expression for $\lambda$:
        \ref{eq:20161031-lambda-is}, one has:
        \begin{equation}
            n_a n_b \chi^a_\mu \chi^b_\mu = \chi^1_\mu\sum_c
            c_{abc}n_c\chi^c_\mu
        \end{equation}
        Now, one can see this pattern and I would not expatiate on
        it. The only remaining elements are equation
        \ref{eq:20161031-x1xa-Ndelta} and the fact that
        \begin{equation}
            c_{abe} = \delta_{b,a^{-1}} n_a
        \end{equation}
        where $e$ is the unit element in group $G$, and $a^{-1}$ is
        the inverse class of $a$. This is like saying that only the
        product of $a$ with its inverse class can have unit elements.
        With these one can easily calculate and get
        \begin{equation}
            \sum_{\mu \in \text{I.R.}} \chi^{a*}_\mu\chi^b_\mu = 
            \frac{|G|}{n_a} \delta^{ab}
        \end{equation}
        So we have:
        \begin{equation}
            \sqrt{\frac{n_a}{|G|}}(\chi^a_1,\chi^a_2,\cdots,\chi^a_r)
        \end{equation}
        a series of $k$ orthonomal $r$-dimensional vectors. Hence
        \begin{equation}
            k\leq r
        \end{equation}
        Then, together with previous result, we have:
        \begin{equation}
            r = k
        \end{equation}
    \end{proof}
% 1. 自共轭 iff 特征 实数
% 2. 非自共轭 至少一个群元 复数 -》 成对出现
% 3. 实表示 是 自共轭
% 4. 特征 实数 不一定 实表示 (so 有 自共轭 但非 实的表示)
% 5. thm 5 on pp. 68.
